Selective electroporation of the viral envelope

### 2021-04-19 documents/pure_electroporation.tex
Apparent success once again?

>>>>

For use with GEKKO, the transfer function was converted into a system of differential equations:

For PSOPT, a further modification was needed, as the library does not support the derivative of the control during .

Initial guess of 0 produces a trap.

because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
PSOPT [] with IPOPT\cite{implementation2006} solver.
